comgen-outline

### 2017-06-13 paper/comgen-paper.Rmd
fix minor bug in habituals data processing
begin constructing habituals inset figs

```{r include = FALSE}

```{r libraries}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(tidyr)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "../"
options("scipen"=10) 
```

@@

```{r habituals-prior-model-run}
items <- levels(d.hab.priors.filtered$item)
n_samples <- 500
rs.habituals.bda.prior <- data.frame()

@@

```
```{r habituals-endorsement-figure, fig.width=11, fig.height=8}
grid.arrange(fig.habituals.endorsement.vs.freq, 
             habituals.endorsement.models,
             generics.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

>>>>

```{r libraries}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "../"
options("scipen"=10) 
```

@@

```{r habituals-prior-model-run, cache = T}
items <- levels(factor(d.hab.priors.filtered$item))
n_samples <- 500
rs.habituals.bda.prior <- data.frame()

@@

```{r habituals-simulation-model, eval = F}
l0.hab.model <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "habitual";

var lowerBound = -5, upperBound = 10, binWidth = 0.5;

var stateBins =  _.range(
  lowerBound, upperBound, binWidth
)

var thetaBins = map2(function(b1, b2){
  var diff = Math.abs(b2 - b1) / 2;
  return roundTo3(diff+ b1);
}, stateBins(0, stateBins.length-1), stateBins.slice(1))

var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state> _.min(thetaBins):
         true
}

  {
    "action": "climbs mountains",
    "mixture_female_mean": 0.0949,
    "mixture_female_samplesize": 3.7153,
    "mixture_male_mean": 0.0566,
    "mixture_male_samplesize": 0.9652,
    "stableFreq_female_mean": 0.3953,
    "stableFreq_female_samplesize": 1.6992,
    "stableFreq_male_mean": 0.8339,
    "stableFreq_male_samplesize": 1.5171
  }
]

var stable_female = beta({
  a: mixture_female_mean * mixture_female_samplesize,
  b: (1 - mixture_female_mean) * mixture_female_samplesize
})

var stable_male = beta({
  a: mixture_male_mean * mixture_male_samplesize,
  b: (1 - mixture_male_mean) * mixture_male_samplesize
})

var statePrior = Infer({model: function(){
  var gender = flip(0.5) ? "female" : "male";
  return gender == "female" ?
    flip(stable_female) ? 
      categorical({
        vs: stateBins,
        ps: map(function(b) {
          return probability(Gaussian({
                mu: stableFreq_female_mean, 
                sigma: stableFreq_female_samplesize
          }), b) + Number.EPSILON
        }, stateBins )
      }) :
    _.min(stateBins) : 
    flip(stable_male) ? 
      categorical({
        vs: stateBins,
        ps: map(function(b) {
          return probability(Gaussian({
                mu: stableFreq_male_mean, 
                sigma: stableFreq_male_samplesize
          }), b) + Number.EPSILON
        }, stateBins )
      }) :
    _.min(stateBins)
}});

//var out = {generic: listener0("generic"), some: listener0("some")}
//out
continuousListener0(data.utt[0])
'
```

```{r habituals-model-insets, fig.width = 4.75, fig.height = 1.5, eval = F}
example.habituals.actions <- separate(data.frame(example.habituals), 
                                      example.habituals, 
                                      into=c("action", "time_period"), sep = "_")$action

m.hab.fullmodel.prior.parameters <- m.hab.samp %>%
  filter(type == "prior", B %in% example.habituals.actions) %>%
  rename(action = B, variable = C, gender = D, parameter = E) %>%
  group_by(action, variable, gender, parameter) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.hab.fullmodel.prior.parameters.tidy <- m.hab.fullmodel.prior.parameters %>%
  ungroup() %>%
  select(action, variable, gender, parameter, MAP) %>%
  mutate(param = paste(variable, gender, parameter, sep = "_")) %>%
  select(-variable, -gender, -parameter) %>%
  spread(param, MAP)

hab.listener.predictions <- data.frame()

for (p in example.habituals.actions){
 priorParams <- m.hab.fullmodel.prior.parameters.tidy %>% filter(action == p)

 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "habitual")

 l0.rs <- webppl(l0.hab.model, data = inputData, data_var = "data")

 hab.listener.predictions <- bind_rows(
   hab.listener.predictions, 
   l0.rs %>% select(Parameter,value) %>% mutate(action = p)
   )

}

```{r habituals-endorsement-figure, fig.width=11, fig.height=8}
grid.arrange(fig.habituals.endorsement.vs.freq, 
             habituals.endorsement.models,
             generics.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```
